The Astropy Project

### 2017-10-31 main.tex
affiliated package table in landscape mode
change table to deluxetable environment
opening quote

The \astropypkg core package documentation contains narrative descriptions of
the package functionality along with detailed usage notes for functions,
classes, and modules.
While useful as a reference and for more advanced \python users, it is not the
right entry-point for all users or learning environments.
In the near future, we will launch a new resource for learning to use both the
\astropypkg core package and the many packages in the broader \astropy
ecosystem, under the name '\emph{Learn Astropy}.'

@@

\begin{table}[h]
  \centering
  \caption{Registry of affiliated packages.}
  \label{tab:registry}
  \begin{tabular}{ccccc}
    \toprule
    Package Name  & Stable & PyPI Name & Maintainer & Citation \\
    \midrule
      \input{registry.tex}
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[h]
  \centering
  \caption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
  \begin{tabular}{cccc}
    \toprule
    Package Name  & Stable & PyPI Name & Maintainer \\
    \midrule
      \input{registry_prov.tex}
    \bottomrule
  \end{tabular}
\end{table}

>>>>

The \astropypkg core package documentation contains narrative descriptions of
the package functionality along with detailed usage notes for functions,
classes, and modules.
While useful as a reference and for more advanced \python users, it is not the
right entry-point for all users or learning environments.
In the near future, we will launch a new resource for learning to use both the
\astropypkg core package and the many packages in the broader \astropy
ecosystem, under the name `\emph{Learn Astropy}.'

@@

\begin{longrotatetable}
  \begin{deluxetable*}{ccccc}
    \tablecaption{Registry of affiliated packages.}
    \label{tab:registry}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer} &
        \colhead{Citation}
      }
      \startdata
        \input{registry.tex}
      \enddata
  \end{deluxetable*}
\end{longrotatetable}

\begin{deluxetable*}{cccc}
  \tablecaption{Registry of provisionally accepted affiliated packages.}
  \label{tab:registry_prov}
    \tablehead{
        \colhead{Package Name} &
        \colhead{Stable} &
        \colhead{PyPI Name} &
        \colhead{Maintainer}
      }
    \startdata
      \input{registry_prov.tex}
    \enddata
\end{deluxetable*}
